%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{utils}
\usepackge{csquotes}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\cvheader

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    I pride myself in being a highly motivated and diligent individual able to
    acquire any skill. Aside from education and computing, I was involved with
    sports from an early age, helping me develop great perseverance and team
    working skills. 

    I started programming at age ten after wanting to keep track of the
    football matches I played with friends. Starting in \texttt{Microsoft Excel}, I
    quickly learned \texttt{Visual Basic} to help enhance its functionality.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \begin{barchart}{5.5}
        \baritem{Python}{70}
        \baritem{GoLang}{50}
        \baritem{TypeScript}{90}
        \baritem{JavaScript}{90}
        \baritem{PHP}{90}
        \baritem{Bash}{70}
        \baritem{Others}{40}
    \end{barchart}
\end{minipage}

\begin{minipage}[t]{0.5\textwidth} % 40% of the page width for the introduction text
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \vspace{10mm}
    \begin{itemize}
        \item Passionate about development
        \item Passionate about security
        \item Enthusiastic and motivated 
        \item Capacity and desire to continue learning
        \item Ability to write testable code
        \item Ability to communicate with developers
    \end{itemize}
\end{minipage}
% \hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
    \vspace{5mm}
    \begin{itemize}
        \item Ability to write formal specifications 
        \item Ability to communicate with none technical peers
        \item Ability to work to set timescales
        \item Ability to estimate timescales 
        \item Ability to work as part of a team
        \item Ability to work self-sufficiently
    \end{itemize}
\end{minipage}

\vspace{10mm}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
    \entry
    {2013 -- 2015}
    {Diploma of Higher Education in Computing}
    {Teesside University}
    {}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
    \entry 
    {2021 - Feb 2022\\\footnotesize{5 Months}} 
    {Full-stack developer} {KitchenCut} 
    { 
        Within the agile methodology I implemented multiple performant third
        party integrations, while also supporting other parts of the
        application. Including security fixes and front-end improvements.
        \texttt{PHP}\slashsep\texttt{JavaScript}\slashsep\texttt{Laravel}\slashsep
        \texttt{Multi-tenancy}\slashsep\texttt{MYSQL}\slashsep\texttt{Docker}
        \slashsep\texttt{Git}
    } 
    \entry 
    {2020 -- April 21\\\footnotesize{9 Months}}
    {Full-stack developer} {PlanHappy Limited}
    {
        Working with an agile methodology, my role entailed executing tasks
        published on the development board, while trying to champion solutions that
        all the stakeholders are happy with. Projects ranged from migrations and
        general administrative pages to the continuous integration pipeline.
        \texttt{PHP}\slashsep\texttt{PHPUnit}\slashsep\texttt{JavaScript}\slashsep
        \texttt{Laravel}\slashsep\texttt{Multi-tenancy}\slashsep\texttt{Postgres}
        \slashsep\texttt{Docker}\slashsep\texttt{Git}
    }
    \entry 
    {2019 -- June 2020\\\footnotesize{9 Months}}
    {Full-stack developer} {Imprint Group}
    {
        During this time I was a part of a team in the process of re-writing an
        e-commerce application using the Symfony framework. My role was mainly
        re-writing parts of the legacy system on both the front and back-end
        and integrating with third party systems.
        \texttt{Vue 2}\slashsep\texttt{PHP}\slashsep\texttt{PHPUnit}\slashsep
        \texttt{TypeScript 3}\slashsep\texttt{Symfony}\slashsep
        \texttt{Multi-tenancy}\slashsep\texttt{Doctrine}\slashsep\texttt{MariaDB}
        \slashsep\texttt{Docker}\slashsep\texttt{Git}
    }
    \entry
    {2017 -- mid 2019\\\footnotesize{2 Years}} 
    {Full-stack developer} {VisualSoft}
    {
        Whilst at VisualSoft I was a part of the Enterprise Technical Support
        team. My role was mainly to support existing and new developments, as
        well as suggesting and implementing improvements. I also tutored the
        junior PHP and front-end developers, along with a range of projects
        focused on issues requiring an understanding of both the front and
        back-end.
        \texttt{ES3}\slashsep\texttt{JQuery}\slashsep\texttt{PHP}\slashsep
        \texttt{PHPUnit}\slashsep\texttt{MYSQL}\slashsep\texttt{Node}\slashsep
        \texttt{Git}\slashsep\texttt{Redis}\slashsep\texttt{Varnish}\slashsep
        \texttt{CI}
    }
    \entry 
    {2010 -- 2017\\\footnotesize{part time}}
    {Computing Assistant} {K M Snowdon Builders}
    {
        My role encompassed a large variety of tasks, from marketing and sales, to
        programming in various languages, creating multiple websites, services and
        the small office network.
        \texttt{PHP}\slashsep\texttt{Flash}\slashsep\texttt{JQuery}\slashsep
        \texttt{MYSQL}
    }
\end{entrylist}

\cvsect{Hobby Projects}
\begin{entrylist}
    \entry {2017 -- present}{Hobby continued}{}
    {
        I have focused on distributed systems, cyber security, and the
        implications of legislation on systems design. While using a variety of
        languages and programming styles.
        \texttt{GoLang}\slashsep\texttt{Python}\slashsep\texttt{Linux}
        \slashsep\texttt{SOA}\slashsep\texttt{Microservices}\slashsep\texttt{Virtualization}
    }
    \entry {2006 -- 2017}{Hobby}{}
    {
        My research has ranged more topics than I would care to list, however
        most notably on progressive web applications and \enquote{real time} systems.
        \texttt{Docker}\slashsep\texttt{Redis}\slashsep\texttt{Angular}
        \slashsep\texttt{Vue}\slashsep\texttt{Laravel}\slashsep
        \texttt{Architecture}\slashsep\texttt{Python}\slashsep\texttt{GoLang}
        \slashsep\texttt{Java}
    }
    \entry {2017} {Repositories Helper} {}
    {
        Two words \enquote{repository fatigue}, so I created a program that worked
        similar to the GitHub CLI (before it was released), with some additional
        features that allowed me to sync repositories between systems and act
        upon them as an aggregate. This tool emulates a normal bash workflow and
        building it was more about learning version control tooling than creating
        something with real practical applications.
        \texttt{Git}\slashsep\texttt{Node}
    }
    \entry {2016} {Real Time Spreadsheet} {}
    {
        I created a proof of concept real time application, with near full excel
        formula support. It had full authenticated user and team support, along
        with a number of features: an API builder which populated a form builder,
        shareable links, team management, and a full presence system. The idea
        was to allow team members to also be a IOT device, allowing the formulas
        to preform arbitrary reporting functions. Due to the computational cost
        of server side functions on each update, I opted for the more rational
        approach of in-memory browser computation. To be honest this project
        spanned multiple years and several iterations of other programs that
        started with a PHP script providing CMS functionality, and slowly took on
        extra roles. Creating many versions using multiple languages allowed me to
        assess the landscape in full.
        \texttt{Firebase}\slashsep\texttt{NOSQL}\slashsep\texttt{Polymer}\slashsep
        \texttt{PWA}\slashsep\texttt{ES6}
    }
\end{entrylist}


%----------------------------------------------------------------------------------------

\vspace{1cm}

\cvfooter

\end{document}
